Differentiation with respect to weights for a `hyper3` object

### 2024-05-28 inst/grad_weight.Rmd
multiple probabilities in the argument

```{r,label=definegws}
grad_weight_single <- function(H, probs, wpv, wanted){
  jj <- H[wpv]
  alpha <- drop(powers(jj))
  powers(jj) <- -1
  jj[setNames(1,wanted)] <- +1
  pnames(jj) <- pnames(H)
  alpha*loglik(probs,jj,log=FALSE)
  }
```

@@

If we wish to differentiate with respect to `D` we need a different technique (TBA).

>>>>

```{r,label=definegws}
grad_weight_single <- function(H, probs, wpv, wanted){
  jj <- H[wpv]
  alpha <- drop(powers(jj))
  powers(jj) <- -1
  jj[setNames(rep(1,length(wanted)),wanted)] <- +1
  pnames(jj) <- pnames(H)
  alpha*loglik(probs,jj,log=FALSE)
  }
```

@@

If we wish to differentiate with respect to `D` we need a slight
generalization, specifically that the `wanted` argument is length 2:

```{r label=diffD}
diff <- (
 grad_weight_single(H, probs, c(p1=  D,p2=  D), c("p1","p2")) +
 grad_weight_single(H, probs, c(p1=w+D,p2=1+D), c("p1","p2")) +
 grad_weight_single(H, probs, c(p1=1+D,p2=w+D), c("p1","p2"))
 )

LHS <- diff  # using grad_weight_single()
dD <- 1e-4
RHS <- (loglik(probs,f2(w,D=D+dD/2)) - loglik(probs,f2(w=w,D=D-dD/2)))/dD  # d/dD via numerics
c(LHS,RHS,LHS-RHS)
```
